05_accessibility_measure_calcs

### 2024-11-04 data-raw/04_accessibility_measure_calcs.qmd
Added grocery travel time tables

<!--

**WARNING**: The travel time matrices for 12 pm are missing.

```{r}
#| eval: false
ttm_small_path <- fs::dir_create("./ttms_12pm")

ttm_12pm_folders <- fs::dir_ls("./ttms", 
                               type = "directory", 
                               regexp = "12_00_00", 
                               recurse = TRUE)

walk(ttm_12pm_folders, ~dir_copy(.x, fs::path(ttm_small_path, (.x)), overwrite = TRUE))
```

@@

Assigning grocery store related travel impedance weights, for now, from Kwan 1998
```{r}
b0 <- 180
travel_matrix_grocer <- travel_matrix_grocer |>  
  mutate(
    o_j = 1, # opportunity intensity of each grocery store is 1
    f = exp(-travel_time_p50 ^ 2 / b0) #informed by Kwan 1998) 
    )
```

## grocer spatial accessibility

Let's also add non-competitive grocery store spatial accessibility to the frame:
```{r}
access_grocers_2019 <- travel_matrix_grocer_2019 |> group_by(from_id) |> summarise(S_i = sum(f*o_j))
access_grocers_2023 <- travel_matrix_grocer_2023 |> group_by(from_id) |> summarise(S_i = sum(f*o_j))

#also adding per capita spatial accessibility 
spatial_mea_grocers_2019_DA <- spatial_mea_grocers_2019_DA |> left_join(access_grocers_2019, by="from_id") |>
  mutate(s_i = S_i/Population)
spatial_mea_grocers_2023_DA <- spatial_mea_grocers_2023_DA |> left_join(access_grocers_2023, by="from_id") |>
  mutate(s_i = S_i/Population)
```
```{r}
#to save space, remove ttms grocers
rm(travel_matrix_grocer, travel_matrix_grocer_2019, travel_matrix_grocer_2023)
```
-->

# Accessibility to employment

>>>>

@@

Save matrices with travel time to groceries:
```{r}
regions <- levels(as.factor(travel_matrix_grocer$region))

for(i in regions){
  travel_matrix_grocer |>
    filter(region == i) |>
    assign(x = glue::glue("travel_matrix_grc_{i}"),
         value = _)

  save(list = glue::glue("travel_matrix_grc_{i}"),
       file = glue::glue(here::here(),
                       "/data/travel_matrix_grc_{i}.rda"),
     compress = "xz")
}

<!--
Assigning grocery store related travel impedance weights, for now, from Kwan 1998
```{r}
b0 <- 180
travel_matrix_grocer <- travel_matrix_grocer |>  
  mutate(
    o_j = 1, # opportunity intensity of each grocery store is 1
    f = exp(-travel_time_p50 ^ 2 / b0) #informed by Kwan 1998) 
    )
```
-->

# Travel time to employment
